The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
tidy manuscript

We altered social scale based on visual (short distance) and auditory (long
distnace) sensory modalities of caribou (REF?). Specifically, we modified the
distance threshold required for group assignment (see above) and re-assigned
groups at incremental distance between 5-500m. For example, at the finest social
scale, only individuals within 5m of one another were considered in the same
group, whereas at the coarset social scale, only individuals within 500m of one
another were considered in the same group.

@@

To assess the influence of spatial scale on multilayer networks, we re-sampled
our landcover classification map at varying scales. Specifically, we selected
scales relevant to caribou ecology. We re-sampled landcover using the
`grainchanger` **package** (Graham 2019) at **five** scales: 100m, 250m, 500m,
1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for
caribou during foraging (REF), while re-sampling at 1000m and 2500m represents
the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau
et al. 2017). Resampling occurred based on a modal moving window method, where
**XXXXX. [ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]**

@@

**Observational scale** (temorary header): Studies of social network analysis
vary in the number and frequency of observations as well as the data collection
technique used to generate networks (Davis et al. 2018; Webber and Vander Wal
2019).

Randomly select max number of observations - timegroups -  (right now 750). For
each iteration, include n observations for each season for all individuals.
Subsequent iterations include nstep more (right now 25), along with previously
included to remove stochasticity. Parallels with observation data.

@@

Social network structure depends on the timeframe of observation, which can make
networks difficult to compare (Castles et al., 2014). Furthermore, social
network structure can vary seasonally and indicate social environments that an
individual experiences (e.g. Brent, MacLarnon, Platt, & Semple, 2013; Hamede,
Bashford, McCallum, & Jones, 2009; Holekamp, Smith, Strelioff, Van Horn, &
Watts, 2012), or they can be consistent across time, which can be used to
reflect social phenotypes (Aplin et al., 2015; Stanley, Mettke-Hofmann, Hager, &
Shultz, 2018). Seasonal fluctuations have the potential to have disease
transmission and fitness effects for individuals (Balasubramaniam et al., 2019;
Chen et al., 2014). **[QW: I'm not sure what this paragraph adds - I think if we
need to save space we could cut it]**

@@

>>>>

We altered social scale based on visual (short distance) and auditory (long
distnace) sensory modalities of caribou <!--(REF?)-->. Specifically, we modified the
distance threshold required for group assignment (see above) and re-assigned
groups at incremental distance between 5-500m. For example, at the finest social
scale, only individuals within 5m of one another were considered in the same
group, whereas at the coarset social scale, only individuals within 500m of one
another were considered in the same group.

@@

To assess the influence of spatial scale on multilayer networks, we re-sampled
our landcover classification map at varying scales. Specifically, we selected
scales relevant to caribou ecology. We re-sampled landcover using the
`grainchanger` **package** (Graham 2019) at **five** scales: 100m, 250m, 500m,
1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for
caribou during foraging <!--(REF)-->, while re-sampling at 1000m and 2500m represents
the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau
et al. 2017). Resampling occurred based on a modal moving window method, where
**XXXXX. [ALEC YOU'RE GOING TO HAVE TO ADD DETAIL HERE]**

@@

**Observational scale** <!--(temorary header)-->: Studies of social network analysis
vary in the number and frequency of observations as well as the data collection
technique used to generate networks (Davis et al. 2018; Webber and Vander Wal
2019).

Randomly select max number of observations - timegroups - <!-- (right now 750)-->. For
each iteration, include n observations for each season for all individuals.
Subsequent iterations include nstep more <!--(right now 25)-->, along with previously
included to remove stochasticity. Parallels with observation data.

@@

Social network structure depends on the timeframe of observation, which can make
networks difficult to compare (Castles et al., 2014). Furthermore, social
network structure can vary seasonally and indicate social environments that an
individual experiences (e.g. Brent, MacLarnon, Platt, & Semple, 2013; Hamede,
Bashford, McCallum, & Jones, 2009; Holekamp, Smith, Strelioff, Van Horn, &
Watts, 2012), or they can be consistent across time, which can be used to
reflect social phenotypes (Aplin et al., 2015; Stanley, Mettke-Hofmann, Hager, &
Shultz, 2018). Seasonal fluctuations have the potential to have disease
transmission and fitness effects for individuals (Balasubramaniam et al., 2019;
Chen et al., 2014). <!-- **[QW: I'm not sure what this paragraph adds - I think if we
need to save space we could cut it]**-->

@@

<!-- add jack -->
